\documentclass{article}
\usepackage{times}
\textwidth 130mm
\textheight 188mm
\footskip 8mm
\parindent 0in
\newcommand{\writetitle}[2]{
\addcontentsline{toc}{part}{\normalsize{{\it #2}\\#1}\vspace{-17pt}}\vskip 2em
\begin{center}{\Large {\bf #1} \par}\vskip 1em{\large\lineskip .5em{\bf #2}\par}
\end{center}\vskip .5em}
	
\begin{document}

\writetitle{Server Side Vote Clustering in Human-Computer Distributed Computing}
{Petar Tomov, Iliyan Zankinski, Todor Balabanov \textsuperscript{0000-0003-3139-069X}}
% p.tomov@iit.bas.bg iliyan@hsi.iccs.bas.bg todorb@iinf.bas.bg
% Institute of Information and Communication Technologies
% Bulgarian Academy of Sciences
% acad. Georgi Bonchev Str., block 2, office 514, 1113 Sofia, Bulgaria
% http://www.iict.bas.bg/

\underline{Introduction} \\

In the field of distributed computing there is a special branch in which human brain capabilities are involved in order complex task to be solved. Generally distributed computing is used in complex task where desktop computers and even supercomputers are not able to calculate the results in acceptable amount of time or in acceptable calculations price. In order particular problem to fit in distributed computing system such problem should fit in the class of parallel algorithms. It means that different steps in the calculations should have certain degree of independence as instructions flow. The main differences between parallel computing and distributed computing is that distributed systems are heterogeneous with network latency, without central clock and in most cases calculating nodes are not under our own control. \\

Distributed computing becomes invaluable when calculated problems are outside of the capabilities available in the modern computers. The brightest example for such situation is when subjective human opinion is needed for evolution of beauty. One of the most famous human-distributed computing projects is the Electric Sheep Screensaver (Scott Draves 1999). In this project artificial animals are generated in the form of fractal animations. These artificial individuals are evolved with genetic algorithms. The key point in this project is that the fitness value for genetic algorithm individuals is calculated by users voting. If the user likes the animated he/she votes with thumb-up. If the user dislike the animation he/she votes with thumb-down. The vote of the users is collected on the server side and it is used for the genetic algorithms evolution process. Subjective opinion for beauty of many different people is the key element in creation of such computer generated art. \\

The usage of artificial neural networks in financial forecasting as distributed computing was well presented in the MoneyBee project (Andreas Bohn \& Till Mansmann 1999). Training of artificial neural networks is a task with very high degree of possibilities in parallel calculations and that is why it is so proper for distributed solution. The project was organized as screen-saver for donated calculating power. Weights of the artificial neural networks were improved in the idle periods of participants computer usage. The success of MoneyBee project was taken for a base in VitoshaTrade project (Todor Balabanov 2009). In VitoshaTrade artificial neural networks are trained as background process in MetaTrader 4 trading platform. The concept of screen-saver was changed with background process of a running application. With the expansion of mobile devices in VitoshaTrade project Android Active Wallpaper interface was promoted. By this step calculations were moved from background process of a running application to background service of Android OS wallpaper. The biggest advantages in mobile distributed computing are that devices are operating in 24/7 mode and mobile devices are much more in number than desktop computers.

\vspace*{3mm}
\underline{Vote Clustering with Self-Organizing Maps} \\

\vspace*{3mm}
\underline{Conclusions} \\

Human-computer distributed computing can be very promising tool for financial forecasting. Trading intuition is something that is not achievable with the nowadays computers. Aggregated opinion of group of people in combination with their knowledge and subconscious information processing can lead to much more reliable forecast results. With the support of modern mobile devices and wireless communication channels human-computer based distributed computing becomes widely accessible and cost effective. 

\vspace*{3mm}
\underline{Acknowledgments} \\

This work was supported by private funding of Velbazhd Software LLC.

\vspace*{3mm}
\underline{References} \\

[Scott Draves 1999] Scott Draves: Electric Sheep, http://www.electricsheep.org/

[Andreas Bohn \& Till Mansmann 1999] Andreas Bohn, Till Mansmann: MoneyBee, i42 GmbH, http://us.moneybee.net/

[Todor Balabanov 2009] Todor Balabanov: Vitosha Trade, http://vitoshatrade.veldsoft.eu/

\end{document}

